---
title: "Bjerregaard Pan HLA"
author: "P Buckley"
date: "03/06/2020"
output: bookdown::html_document2
---

## Import packages

```{r setup,message=FALSE}
library(pROC)
library(ggpubr)
library(Biostrings)
library(data.table)
library(dplyr)
library(caret)
library(purrr)

library(tidyverse)
library(yardstick)
library(foreach)
library(doParallel)
library(stringdist)

options(tibble.pillar.subtle=FALSE, tibble.pillar.sigfig=9, tibble.pillar.min_title_chars=10)

```

# Prepare the data 
```{r,message=FALSE,warning=FALSE}

FullDataset = fread("Nonameric_WT_Mutant.csv") %>% dplyr::rename(immunogenicity_binary=`Immunogenic (1=yes)`,WT_Peptide=`Wild type peptide`,Peptide=`Mutant peptide`) %>% mutate(Immunogenicity=ifelse(immunogenicity_binary==1,"Positive","Negative")) %>% select(!c(`Wild type score`,`Mutant score`))

FullDataset=FullDataset %>% filter(width(Peptide)==9)
FullDataset=FullDataset %>% mutate(HLA_Allele = 'HLA-A02:01')
```

# Functions

```{r}
calculate_f_beta = function(beta, precision, recall) {
   return((beta^2 + 1)*(precision*recall / ((beta^2)*precision + recall)))
}

```


# EDA
- Showing the distribution of data after filtering. Filtering removes contradictory peptides, duplicate peptides, and any neoantigens with more than one mutation.
```{r, fig.width=4,fig.height=5,dev='svg'}

 FullDataset %>% select(Immunogenicity,HLA_Allele) %>% table %>% as.data.table %>% ggbarplot(x="Immunogenicity",y="N",fill="Immunogenicity",label=T,width=0.5) + ylab("Number of Peptides") + xlab("Immunogenicity Classification")+ font("xlab",size=16,color="black")+ font("ylab",size=16,color="black")  + font("legend.text",size=10) + labs(fill="Immunogenicity")

```

# Analysis

```{r}
TrainingData = readRDS("../Analysis_Pan_HLA_Pathogenic/PanHLA_FullDataset.rds")
TrainingData=TrainingData %>% as.data.table

TrainingData=TrainingData %>% filter(!Peptide %in% intersect(TrainingData$Peptide,FullDataset$Peptide))

```

```{r}
combinedData=readRDS(file="PanHLA_Bjerregaard_combinedData.rds")
 # write.table(combinedData,"PanHLA_Bjerregaard_combinedData.txt",sep="\t",row.names = F,quote=F)

```

## Accuracy 
- Calculate pure accuracy and plot in the context of a blind model where all sequences are predicted negative.
```{r,fig.width=8,fig.height=6,message=FALSE,warning=FALSE}

accuracyDF=combinedData %>% group_by(Dataset) %>% summarise(Accuracy=sum(ImmunogenicityPrediction==Immunogenicity)/n())

FullDataset %>% mutate(ImmunogenicityPrediction = 'Negative',Dataset='Blind Model') %>%group_by(Dataset) %>%summarise(Accuracy=sum(ImmunogenicityPrediction==Immunogenicity)/(nrow(FullDataset)))%>% rbind(accuracyDF) %>% ggbarplot(x="Dataset",y="Accuracy",fill="Dataset",palette = "npg",label = TRUE,lab.nb.digits = 4) + ylim(0,1) + rotate_x_text(angle=90)

```

## AUC 
- Compute ROC-AUC. This is not a great metric for imbalanced data but it provides a little context for model comparison.
```{r,fig.width=8,fig.height=6,message=FALSE,warning=FALSE,dev='svg'}
AUCDF = combinedData %>% group_by(Dataset) %>% summarise(ROC=as.numeric(roc(Immunogenicity ~ ImmunogenicityScore)$auc))



NETTEPIAUC=roc(Immunogenicity ~ ImmunogenicityScore,data=combinedData %>% filter(Dataset %in% 'NETTEPI'))
IPREDAUC=roc(Immunogenicity ~ ImmunogenicityScore,data=combinedData %>% filter(Dataset %in% 'IPRED'))
IEDBMODELAUC=roc(Immunogenicity ~ ImmunogenicityScore,data=combinedData %>% filter(Dataset %in% 'IEDB'))
REPITOPE_AUC_CV=roc(Immunogenicity ~ ImmunogenicityScore,data=combinedData %>% filter(Dataset %in% 'REPITOPE'))
NetTepi_NETMHC.AUC.CV = roc(Immunogenicity ~ ImmunogenicityScore,data=combinedData %>% filter(Dataset %in% 'NETTEPI_netMHCpan4'))

roc.AUC=ggroc(list(IEDB_Model=IEDBMODELAUC,iPred=IPREDAUC,NetTepi=NETTEPIAUC,NetTepi_NetMHCpan4=NetTepi_NETMHC.AUC.CV,REpitope=REPITOPE_AUC_CV),legacy.axes = TRUE,size=1.25) + theme_bw() +
  annotate("text",x=.65,y=.185,label=paste0("IEDB:     ",round(auc(IEDBMODELAUC),digits=2),"\n","iPred:     ",round(auc(IPREDAUC),digits=2),"\n","NetTepi: ",round(auc(NETTEPIAUC),digits=2),"\n","NetTepi_NetMHCpan4: ",round(auc(NetTepi_NETMHC.AUC.CV),digits=2),"\n","Repitope: ",round(auc(REPITOPE_AUC_CV),digits=2))) + font("xy.text",size=16,color="black")+ font("xlab",size=16,color="black")+ font("ylab",size=16,color="black") + font("legend.title",color="white") + font("legend.text",size=10) + geom_abline(size=1,intercept = 0, slope = 1,color = "darkgrey", linetype = "dashed")

```


## PR-AUC

```{r,dev='svg'}
combinedData$Immunogenicity = factor(combinedData$Immunogenicity,levels = c("Positive","Negative"))
PR_AUC_COMBINED=combinedData %>% group_by(Dataset) %>% pr_auc(Immunogenicity,ImmunogenicityScore)
PR_AUC_COMBINED$.estimate=round(PR_AUC_COMBINED$.estimate,digits=2)
pr.AUC=combinedData %>% group_by(Dataset) %>% pr_curve(Immunogenicity,ImmunogenicityScore) %>% autoplot() + aes(size = Dataset)+scale_size_manual(values=c(1.25,1.25,1.25,1.25,1.25))+ ggtitle("Precision-Recall Curves") +annotate("text",x=.65,y=.80,label=paste0("IEDB: ",PR_AUC_COMBINED$.estimate[1],"\n","iPred: ",PR_AUC_COMBINED$.estimate[2],"\n","NetTepi: ",PR_AUC_COMBINED$.estimate[3],"\n","NetTepi_NetMHCpan4: ",PR_AUC_COMBINED$.estimate[4],"\n","Repitope: ",PR_AUC_COMBINED$.estimate[5])) + geom_hline(size=1,color="darkgrey",yintercept = nrow(FullDataset[FullDataset$Immunogenicity=='Positive',]) / nrow(FullDataset),linetype="dashed")+ font("xy.text",size=16,color="black")+ font("xlab",size=16,color="black")+ font("ylab",size=16,color="black") + font("legend.title",color="white") + font("legend.text",size=10)
```

## Plot ROC-AUC 

```{r,dev='svg'}
gl <- lapply(list(roc.AUC,pr.AUC), ggplotGrob)
library(grid)
widths <- do.call(unit.pmax, lapply(gl, "[[", "widths"))
heights <- do.call(unit.pmax, lapply(gl, "[[", "heights"))
lg <- lapply(gl, function(g) {g$widths <- widths; g$heights <- heights; g})
grid.newpage()
grid.draw(lg[[1]])

```

## Plot PR-AUC
- Main text Fig 2E

```{r,dev='svg'}
grid.newpage()
grid.draw(lg[[2]])



```


## F1 Score 

```{r,fig.width=8,fig.height=6,message=FALSE,warning=FALSE}

combinedData$Immunogenicity = factor(combinedData$Immunogenicity,levels=c("Positive","Negative"))
combinedData$ImmunogenicityPrediction = factor(combinedData$ImmunogenicityPrediction,levels=c("Positive","Negative"))

F1SCORE=combinedData %>% group_by(Dataset) %>% dplyr::summarise(F1_SCORE= confusionMatrix(positive = "Positive",mode = "prec_recall",
                                                                           reference=Immunogenicity,ImmunogenicityPrediction)$byClass["F1"])                         
```

## Precision 

```{r,fig.width=8,fig.height=6,message=FALSE,warning=FALSE}


PRECISIONCV=combinedData %>% group_by(Dataset) %>% dplyr::summarise(Precision= confusionMatrix(positive = "Positive",mode = "prec_recall",
                                                                           reference=Immunogenicity,ImmunogenicityPrediction)$byClass["Precision"])                           
```


## Recall 

```{r,fig.width=8,fig.height=6,message=FALSE,warning=FALSE}


RECALLCV=combinedData %>% group_by(Dataset) %>% dplyr::summarise(Recall= confusionMatrix(positive = "Positive",mode = "prec_recall",
                                                                           reference=Immunogenicity,ImmunogenicityPrediction)$byClass["Recall"]) %>% as.data.table       
```

## Balanced accuracy 

```{r baancedacc,fig.width=8,fig.height=6,message=FALSE,warning=FALSE}



BALACCURACYCV=combinedData %>% group_by(Dataset) %>% dplyr::summarise(BalancedAccuracy= confusionMatrix(positive = "Positive",mode = "prec_recall",
                                                                           reference=Immunogenicity,ImmunogenicityPrediction)$byClass["Balanced Accuracy"])                                                                           

```

```{r}
F0.5SCORE=inner_join(RECALLCV,PRECISIONCV) %>% group_by(Dataset) %>% dplyr::summarise(F_0.5 = calculate_f_beta(0.5,Precision,Recall))
```

## Visualisation of all key metrics.

```{r UNBALSFACETWRAPCVDATA,fig.height=8,fig.width=9}

accuracyDF %>% inner_join(F1SCORE) %>% inner_join(PRECISIONCV) %>% inner_join(RECALLCV) %>% inner_join(F0.5SCORE) %>% inner_join(BALACCURACYCV) %>% melt(variable.name="Metric") %>% ggbarplot(
  x="Dataset",y="value",fill="Metric",label = T,lab.nb.digits = 2
) + facet_wrap(~Metric) + rotate_x_text(angle=90) + ylim(0,1)
```


# Shuffle the data to create distribution of randomised metric scores
## PR-AUC

```{r,cache=TRUE,fig.cap="Area under the precision-recall curve for a distribution of PR-AUC values after randomising the true classification. Dashed line shows PR-AUC of the predictions made during the benchmarking experiment.",fig.width=6,fig.height=6,dev='svg'}

#setup parallel backend to use many processors
cores=detectCores()
cl <- makeCluster(cores[1]-1) #not to overload your computer
registerDoParallel(cl)

 PR_AUC_RAND.DIST=foreach(i = 1:1000, .combine = rbind,.packages = c("dplyr","magrittr","yardstick","data.table")) %dopar% {
combinedData %>%  group_by(Dataset) %>% mutate(Shuffled_Immunogenicity=sample(size=n(),Immunogenicity))  %>% pr_auc(Shuffled_Immunogenicity,ImmunogenicityScore) %>% mutate(sampleNum=i)
   }

stopCluster(cl)


PR_AUC_COMBINED=combinedData %>% group_by(Dataset) %>% pr_auc(Immunogenicity,ImmunogenicityScore)

PR_AUC_RAND.DIST %>% ggdensity(x=".estimate",y="..density..",fill="Dataset",add="mean",color = "Dataset",alpha=0.2)  + facet_wrap(~Dataset) + geom_vline(data=PR_AUC_COMBINED,aes(xintercept=.estimate),color="black",linetype="dashed") + xlab("Area under the precision-recall curve") + font("xy.text",size=12,color="black")+ font("xlab",size=16,color="black")+ font("ylab",size=16,color="black") + font("legend.title",color="white") + font("legend.text",size=10)+ theme(legend.position = "none")+rotate_x_text(angle=90)



PR_AUC_RAND.DIST %>% group_by(Dataset) %>% dplyr::summarise(Random_mean=mean(.estimate),sd=sd(.estimate)) %>% inner_join(PR_AUC_COMBINED %>% select(!c(.metric,.estimator))) %>% dplyr::rename(Predicted=.estimate) %>% mutate(zscore = round(((Predicted-Random_mean)/sd),2) ) %>% DT::datatable(caption="Mean, sd and zscore to show distance from mean of random distribution")


```

## IEDB Model Confusion Matrix

```{r iedbcmatrix, message=FALSE,warning=FALSE,fig.width=6,fig.height=6,fig.cap="IEDB Confusion Matrix. Color is relative to sensitivity/specificity by proportional outcomes within reference groups",dev='svg'}

CM=confusionMatrix(positive = "Positive",mode = "prec_recall",reference=factor(combinedData %>% filter(Dataset %in% 'IEDB')  %>% select(Immunogenicity) %>% pull(),
                       levels = c("Negative","Positive")),
                       factor(combinedData %>% filter(Dataset %in% 'IEDB') %>% select(ImmunogenicityPrediction) %>% pull(),
                       levels=c("Negative","Positive")))
CM
table=data.frame(CM$table)

plotTable <- table %>%
  mutate(Performance = ifelse(table$Prediction == table$Reference, "Good", "Bad")) %>%
  group_by(Reference) %>%
  mutate(prop = Freq/sum(Freq))


ggplot(data = plotTable, mapping = aes(x = Reference, y = Prediction, fill = Performance, alpha = prop)) +
  geom_tile() +
  geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1,size=8) +
  scale_fill_manual(values = c(Good = "green", Bad = "red")) +
  theme_bw() +
  xlim(rev(levels(table$Reference))) + font("xy.text",size=16,color="black")+ font("xlab",size=16,color="black")+ font("ylab",size=16,color="black") + font("legend.text",size=10)+ ggtitle("IEDB Immunogenicity Model")


```


## NetTepi Confusion Matrix

```{r netTepimatrix, message=FALSE,warning=FALSE,fig.width=6,fig.height=6,fig.cap="NetTepi Confusion Matrix. Color is relative to sensitivity/specificity by proportional outcomes within reference groups",dev='svg'}

CM=confusionMatrix(positive = "Positive",mode = "prec_recall",reference=factor(combinedData %>% filter(Dataset == 'NETTEPI')  %>% select(Immunogenicity) %>% pull(),
                       levels = c("Negative","Positive")),
                       factor(combinedData %>% filter(Dataset == 'NETTEPI') %>% select(ImmunogenicityPrediction) %>% pull(),
                       levels=c("Negative","Positive")))
CM
table=data.frame(CM$table)

plotTable <- table %>%
  mutate(Performance = ifelse(table$Prediction == table$Reference, "Good", "Bad")) %>%
  group_by(Reference) %>%
  mutate(prop = Freq/sum(Freq))


ggplot(data = plotTable, mapping = aes(x = Reference, y = Prediction, fill = Performance, alpha = prop)) +
  geom_tile() +
  geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1,size=8) +
  scale_fill_manual(values = c(Good = "green", Bad = "red")) +
  theme_bw() +
  xlim(rev(levels(table$Reference))) + font("xy.text",size=16,color="black")+ font("xlab",size=16,color="black")+ font("ylab",size=16,color="black") + font("legend.text",size=10)+ ggtitle("NetTepi")


```

```{r ,dev='svg', message=FALSE,warning=FALSE,fig.width=6,fig.height=6,fig.cap="NetTepi Ext Confusion Matrix. Color is relative to sensitivity/specificity by proportional outcomes within reference groups"}

CM=confusionMatrix(positive = "Positive",mode = "prec_recall",reference=factor(combinedData %>% filter(Dataset == 'NETTEPI_netMHCpan4')  %>% select(Immunogenicity) %>% pull(),
                       levels = c("Negative","Positive")),
                       factor(combinedData %>% filter(Dataset == 'NETTEPI_netMHCpan4') %>% select(ImmunogenicityPrediction) %>% pull(),
                       levels=c("Negative","Positive")))
CM
table=data.frame(CM$table)

plotTable <- table %>%
  mutate(Performance = ifelse(table$Prediction == table$Reference, "Accurate", "Inaccurate")) %>%
  group_by(Reference) %>%
  mutate(prop = Freq/sum(Freq))


ggplot(data = plotTable, mapping = aes(x = Reference, y = Prediction, fill = Performance, alpha = prop)) +
  geom_tile() +
  geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1,size=8) +
  scale_fill_manual(values = c(Accurate = "green", Inaccurate = "red")) +
  theme_bw() +
  xlim(rev(levels(table$Reference)))+ font("xy.text",size=16,color="black")+ font("xlab",size=16,color="black")+ font("ylab",size=16,color="black") + font("legend.text",size=10)+ font("xy.text",size=16,color="black")+ font("xlab",size=16,color="black")+ font("ylab",size=16,color="black") + font("legend.text",size=10) + ggtitle("NETTEPI_netMHCpan4")


```

## iPred Confusion Matrix

```{r iPredmatrix, message=FALSE,warning=FALSE,fig.width=6,fig.height=6,dev='svg'}

CM=confusionMatrix(positive = "Positive",mode = "prec_recall",reference=factor(combinedData %>% filter(Dataset %in% 'IPRED')  %>% select(Immunogenicity) %>% pull(),
                       levels = c("Negative","Positive")),
                       factor(combinedData %>% filter(Dataset %in% 'IPRED') %>% select(ImmunogenicityPrediction) %>% pull(),
                       levels=c("Negative","Positive")))
CM
table=data.frame(CM$table)

plotTable <- table %>%
  mutate(Performance = ifelse(table$Prediction == table$Reference, "Good", "Bad")) %>%
  group_by(Reference) %>%
  mutate(prop = Freq/sum(Freq))


ggplot(data = plotTable, mapping = aes(x = Reference, y = Prediction, fill = Performance, alpha = prop)) +
  geom_tile() +
  geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1,size=8) +
  scale_fill_manual(values = c(Good = "green", Bad = "red")) +
  theme_bw() +
  xlim(rev(levels(table$Reference)))+ font("xy.text",size=16,color="black")+ font("xlab",size=16,color="black")+ font("ylab",size=16,color="black") + font("legend.text",size=10) + ggtitle("iPred")


```

## REPITOPE Confusion Matrix

```{r REPITOPEmatrix, message=FALSE,warning=FALSE,fig.width=6,fig.height=6,dev='svg'}

CM=confusionMatrix(positive = "Positive",mode = "prec_recall",reference=factor(combinedData %>% filter(Dataset %in% 'REPITOPE')  %>% select(Immunogenicity) %>% pull(),
                       levels = c("Negative","Positive")),
                       factor(combinedData %>% filter(Dataset %in% 'REPITOPE') %>% select(ImmunogenicityPrediction) %>% pull(),
                       levels=c("Negative","Positive")))
CM
table=data.frame(CM$table)

plotTable <- table %>%
  mutate(Performance = ifelse(table$Prediction == table$Reference, "Good", "Bad")) %>%
  group_by(Reference) %>%
  mutate(prop = Freq/sum(Freq))


ggplot(data = plotTable, mapping = aes(x = Reference, y = Prediction, fill = Performance, alpha = prop)) +
  geom_tile() +
  geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1,size=8) +
  scale_fill_manual(values = c(Good = "green", Bad = "red")) +
  theme_bw() +
  xlim(rev(levels(table$Reference)))+ font("xy.text",size=16,color="black")+ font("xlab",size=16,color="black")+ font("ylab",size=16,color="black") + font("legend.text",size=10) + ggtitle("REpitope")

```
