---
title: "HLA Specific Pathogenic Experiment"
author: "P Buckley"
date: "18/06/2020"
output: bookdown::html_document2
---

## Import packages
```{r setup,message=FALSE}
library(pROC)
library(ggpubr)
library(Biostrings)
library(data.table)
library(dplyr)

library(caret)
library(purrr)

library(tidyverse)
library(yardstick)
library(doParallel)
library(foreach)
library(stringdist)
library(magrittr)

# Scientific notation is turned off as it can tamper with numerics
options(scipen = 999)

```

# Import datasets
- combinedData contains the data generated by the 10-fold cv for each model during this experiment
- FullDataset contains the HLA-specific dataset
```{r}

FullDataset= readRDS("A201_standardData_forAnalysis_BALANCED.rds")
FullDataset = FullDataset %>% as.data.table

combinedData = readRDS("HLASpecific_combinedData.rds") %>% as.data.table

 # write.table(combinedData,"HLASpecific_combinedData.txt",sep="\t",row.names = F,quote=F)
 # write.table(FullDataset,"HLASpecific_FullDataset.txt",sep="\t",row.names = F,quote=F)

```

# Functions

```{r}
# Function to calculate the F score, given beta, precision and recall.
 calculate_f_beta = function(beta, precision, recall) {
   return((beta^2 + 1)*(precision*recall / ((beta^2)*precision + recall)))
 }


```

# Analysis

## Produce ROC-AUC

```{r,message=FALSE}
accuracyDF=combinedData %>% dplyr::group_by(Dataset) %>% summarise(Accuracy=sum(ImmunogenicityPrediction==Immunogenicity)/nrow(FullDataset))

# Create a data table that comprise each model's ROC-AUC=
 AUCDF = combinedData %>% as.data.table %>% group_by(Dataset) %>% summarise(ROC=as.numeric(roc(Immunogenicity ~ ImmunogenicityScore)$auc))

# Produce roc curves for each model 
NETTEPIAUC=roc(Immunogenicity ~ ImmunogenicityScore,data=combinedData %>% filter(Dataset %in% 'NETTEPI'))
IPREDAUC=roc(Immunogenicity ~ ImmunogenicityScore,data=combinedData %>% filter(Dataset %in% 'IPRED'))
IEDBMODELAUC=roc(Immunogenicity ~ ImmunogenicityScore,data=combinedData %>% filter(Dataset %in% 'IEDB'))
REPITOPE_AUC_CV=roc(Immunogenicity ~ ImmunogenicityScore,data=combinedData %>% filter(Dataset %in% 'REPITOPE'))
NetTepi_NETMHC.AUC.CV = roc(Immunogenicity ~ ImmunogenicityScore,data=combinedData %>% filter(Dataset %in% 'NETTEPI_netMHCpan4'))

# Use GGROC to combine and visualise the ROC-AUC curves
roc.AUC=ggroc(list(IEDB_Model=IEDBMODELAUC,iPred=IPREDAUC,NetTepi=NETTEPIAUC,NetTepi_NetMHCpan4=NetTepi_NETMHC.AUC.CV,REpitope=REPITOPE_AUC_CV),legacy.axes = TRUE,size=1.25) + theme_bw() +
  annotate("size"=5,"text",x=.55,y=.185,label=paste0("IEDB:     ",round(auc(IEDBMODELAUC),digits=3),"\n","iPred:     ",round(auc(IPREDAUC),digits=3),"\n","NetTepi: ",round(auc(NETTEPIAUC),digits=3),"\n","NetTepi_NetMHCpan4: ",round(auc(NetTepi_NETMHC.AUC.CV),digits=3),"\n","Repitope: ",round(auc(REPITOPE_AUC_CV),digits=3))) + font("xy.text",size=16,color="black")+ font("xlab",size=16,color="black")+ font("ylab",size=16,color="black") + font("legend.title",color="white") + font("legend.text",size=12) + geom_abline(intercept = 0, slope = 1,color = "darkgrey", linetype = "dashed",size=1)
 
```

## Produce PR-AUC

```{r,fig.width=8,fig.height=6,dev="svg"}
# Calculate PR-AUC for each model
combinedData$Immunogenicity = factor(combinedData$Immunogenicity,levels = c("Positive","Negative"))
PR_AUC_COMBINED=combinedData %>% group_by(Dataset) %>% pr_auc(Immunogenicity,ImmunogenicityScore)
# Round the calculated PR-AUC for plotting
PR_AUC_COMBINED$.estimate=round(PR_AUC_COMBINED$.estimate,digits=3)
# Compute pr-auc for each model, combine and visualise the curves
pr.AUC=combinedData %>% group_by(Dataset) %>% pr_curve(Immunogenicity,ImmunogenicityScore) %>% autoplot() + aes(size = Dataset)+scale_size_manual(values=c(1.25,1.25,1.25,1.25,1.25)) + ggtitle("Precision-Recall Curves") +annotate("size"=5,"text",x=.5,y=.155,label=paste0("IEDB: ",PR_AUC_COMBINED$.estimate[1],"\n","iPred: ",PR_AUC_COMBINED$.estimate[2],"\n","NetTepi: ",PR_AUC_COMBINED$.estimate[3],"\n","NetTepi_NetMHCpan4: ",PR_AUC_COMBINED$.estimate[4],"\n","Repitope: ",PR_AUC_COMBINED$.estimate[5])) + geom_hline(size=1,color="darkgrey",yintercept = nrow(FullDataset[FullDataset$Immunogenicity=='Positive',]) / nrow(FullDataset),linetype="dashed")+ font("xy.text",size=16,color="black")+ font("xlab",size=16,color="black")+ font("ylab",size=16,color="black") + font("legend.title",color="white") + font("legend.text",size=10)
```

## Visualise PR-AUC
```{r,fig.width=8,fig.height=6,dev="svg"}
gl <- lapply(list(pr.AUC,roc.AUC), ggplotGrob)
library(grid)
widths <- do.call(unit.pmax, lapply(gl, "[[", "widths"))
heights <- do.call(unit.pmax, lapply(gl, "[[", "heights"))
lg <- lapply(gl, function(g) {g$widths <- widths; g$heights <- heights; g})
grid.newpage()
grid.draw(lg[[1]])
```

## Visualise ROC-AUC
- Main text Fig 2B

```{r,fig.width=8,fig.height=6,dev="svg"}
grid.newpage()
grid.draw(lg[[2]])

```

## Calculate percentage ROC-AUC differences between Pan-HLA cv and this analysis.

```{r ,fig.width=8,fig.height=6,message=FALSE,warning=FALSE,dev='svg'}
 PerCentageChange= AUCDF %>% mutate(PANHLA=c(0.65,0.701,0.661,0.666,0.756)) %>% group_by(Dataset) %>% dplyr::mutate(PercentageChange=(ROC-PANHLA) / (PANHLA) * (100) )

 PerCentageChange

 PerCentageChange %>% ungroup %>% dplyr::summarise(Mean=mean(PercentageChange),sd=sd(PercentageChange))
 

```

## Extract F1 Scores 

```{r CVF1Score,fig.width=8,fig.height=6,message=FALSE,warning=FALSE}

combinedData$Immunogenicity = factor(combinedData$Immunogenicity,levels=c("Positive","Negative"))
combinedData$ImmunogenicityPrediction = factor(combinedData$ImmunogenicityPrediction,levels=c("Positive","Negative"))

F1SCORE=combinedData %>% group_by(Dataset) %>% dplyr::summarise(F1_SCORE= confusionMatrix(positive = "Positive",mode = "prec_recall",
                                                                           reference=Immunogenicity,ImmunogenicityPrediction)$byClass["F1"])                                                                    
```

## Extract Model Precision 

```{r CVPrecisionScore,fig.width=8,fig.height=6,message=FALSE,warning=FALSE}


PRECISIONCV=combinedData %>% group_by(Dataset) %>% dplyr::summarise(Precision= confusionMatrix(positive = "Positive",mode = "prec_recall",
                                                                           reference=Immunogenicity,ImmunogenicityPrediction)$byClass["Precision"])            

```


## Extract Model Recall 

```{r CVRecallScore,fig.width=8,fig.height=6,message=FALSE,warning=FALSE}


RECALLCV=combinedData %>% group_by(Dataset) %>% dplyr::summarise(Recall= confusionMatrix(positive = "Positive",mode = "prec_recall",
                                                                           reference=Immunogenicity,ImmunogenicityPrediction)$byClass["Recall"]) %>% as.data.table                         

```

## Extract Model Balanced Accuracy 

```{r baancedacc,fig.width=8,fig.height=6,message=FALSE,warning=FALSE}

BALACCURACYCV=combinedData %>% group_by(Dataset) %>% dplyr::summarise(BalancedAccuracy= confusionMatrix(positive = "Positive",mode = "prec_recall",
                                                                           reference=Immunogenicity,ImmunogenicityPrediction)$byClass["Balanced Accuracy"])                                                                           
```

## Calculate Model F0.5 scores

```{r}
F0.5SCORE=inner_join(RECALLCV,PRECISIONCV) %>% group_by(Dataset) %>% dplyr::summarise(F_0.5 = calculate_f_beta(0.5,Precision,Recall))
```

## Visualise all key metrics.

```{r UNBALSFACETWRAPCVDATA,fig.height=8,fig.width=9}

accuracyDF %>% inner_join(F1SCORE) %>% inner_join(PRECISIONCV) %>% inner_join(RECALLCV) %>% inner_join(F0.5SCORE) %>% inner_join(BALACCURACYCV) %>% melt(variable.name="Metric") %>% ggbarplot(
  x="Dataset",y="value",fill="Metric",label = T,lab.nb.digits = 2,alpha=0.6
) + facet_wrap(~Metric) + rotate_x_text(angle=90) + ylim(0,1)
```

## IEDB Model Confusion Matrix

```{r iedbcmatrix, message=FALSE,warning=FALSE,fig.width=6,dev='svg',fig.height=6,fig.cap="IEDB Confusion Matrix. Color is relative to sensitivity/specificity by proportional outcomes within reference groups"}

CM=confusionMatrix(positive = "Positive",mode = "prec_recall",reference=factor(combinedData %>% filter(Dataset %in% 'IEDB')  %>% select(Immunogenicity) %>% pull(),
                       levels = c("Negative","Positive")),
                       factor(combinedData %>% filter(Dataset %in% 'IEDB') %>% select(ImmunogenicityPrediction) %>% pull(),
                       levels=c("Negative","Positive")))
CM
table=data.frame(CM$table)

plotTable <- table %>%
  mutate(Performance = ifelse(table$Prediction == table$Reference, "Accurate", "Inaccurate")) %>%
  group_by(Reference) %>%
  mutate(prop = Freq/sum(Freq))


ggplot(data = plotTable, mapping = aes(x = Reference, y = Prediction, fill = Performance, alpha = prop)) +
  geom_tile() +
  geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1,size=8) +
  scale_fill_manual(values = c(Accurate = "green", Inaccurate = "red")) +
  theme_bw() +
  xlim(rev(levels(table$Reference))) + ggtitle("IEDB Immunogenicity Model")+ font("xy.text",size=16,color="black")+ font("xlab",size=16,color="black")+ font("ylab",size=16,color="black") + font("legend.text",size=10)


```

## NetTepi Confusion Matrix

```{r netTepimatrix, message=FALSE,warning=FALSE,fig.width=6,dev='svg',fig.height=6,fig.cap="NetTepi Confusion Matrix. Color is relative to sensitivity/specificity by proportional outcomes within reference groups"}

CM=confusionMatrix(positive = "Positive",mode = "prec_recall",reference=factor(combinedData %>% filter(Dataset %in% 'NETTEPI')  %>% select(Immunogenicity) %>% pull(),
                       levels = c("Negative","Positive")),
                       factor(combinedData %>% filter(Dataset %in% 'NETTEPI') %>% select(ImmunogenicityPrediction) %>% pull(),
                       levels=c("Negative","Positive")))
CM
table=data.frame(CM$table)

plotTable <- table %>%
  mutate(Performance = ifelse(table$Prediction == table$Reference, "Accurate", "Inaccurate")) %>%
  group_by(Reference) %>%
  mutate(prop = Freq/sum(Freq))


ggplot(data = plotTable, mapping = aes(x = Reference, y = Prediction, fill = Performance, alpha = prop)) +
  geom_tile() +
  geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1,size=8) +
  scale_fill_manual(values = c(Accurate = "green", Inaccurate = "red")) +
  theme_bw() +
  xlim(rev(levels(table$Reference))) + ggtitle("NetTepi")+ font("xy.text",size=16,color="black")+ font("xlab",size=16,color="black")+ font("ylab",size=16,color="black") + font("legend.text",size=10)

```

## NETTEPI_netMHCpan4 Confusion Matrix

```{r, dev='svg', message=FALSE,warning=FALSE,fig.width=6,fig.height=6,fig.cap="NetTepi Confusion Matrix. Color is relative to sensitivity/specificity by proportional outcomes within reference groups"}

CM=confusionMatrix(positive = "Positive",mode = "prec_recall",reference=factor(combinedData %>% filter(Dataset == 'NETTEPI_netMHCpan4')  %>% select(Immunogenicity) %>% pull(),
                       levels = c("Negative","Positive")),
                       factor(combinedData %>% filter(Dataset == 'NETTEPI_netMHCpan4') %>% select(ImmunogenicityPrediction) %>% pull(),
                       levels=c("Negative","Positive")))
CM
table=data.frame(CM$table)

plotTable <- table %>%
  mutate(Performance = ifelse(table$Prediction == table$Reference, "Accurate", "Inaccurate")) %>%
  group_by(Reference) %>%
  mutate(prop = Freq/sum(Freq))


ggplot(data = plotTable, mapping = aes(x = Reference, y = Prediction, fill = Performance, alpha = prop)) +
  geom_tile() +
  geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1,size=8) +
  scale_fill_manual(values = c(Accurate = "green", Inaccurate = "red")) +
  theme_bw() +
  xlim(rev(levels(table$Reference)))+ font("xy.text",size=16,color="black")+ font("xlab",size=16,color="black")+ font("ylab",size=16,color="black") + font("legend.text",size=10) + ggtitle("NETTEPI_netMHCpan4")


```

## iPred Confusion Matrix

```{r iPredmatrix, message=FALSE,warning=FALSE,fig.width=6,dev='svg',fig.height=6,fig.cap="iPred Confusion Matrix. Color is relative to sensitivity/specificity by proportional outcomes within reference groups"}

CM=confusionMatrix(positive = "Positive",mode = "prec_recall",reference=factor(combinedData %>% filter(Dataset %in% 'IPRED')  %>% select(Immunogenicity) %>% pull(),
                       levels = c("Negative","Positive")),
                       factor(combinedData %>% filter(Dataset %in% 'IPRED') %>% select(ImmunogenicityPrediction) %>% pull(),
                       levels=c("Negative","Positive")))
CM
table=data.frame(CM$table)

plotTable <- table %>%
  mutate(Performance = ifelse(table$Prediction == table$Reference, "Accurate", "Inaccurate")) %>%
  group_by(Reference) %>%
  mutate(prop = Freq/sum(Freq))


ggplot(data = plotTable, mapping = aes(x = Reference, y = Prediction, fill = Performance, alpha = prop)) +
  geom_tile() +
  geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1,size=8) +
  scale_fill_manual(values = c(Accurate = "green", Inaccurate = "red")) +
  theme_bw() +
  xlim(rev(levels(table$Reference))) + ggtitle("iPred")+ font("xy.text",size=16,color="black")+ font("xlab",size=16,color="black")+ font("ylab",size=16,color="black") + font("legend.text",size=10)


```

## REPITOPE Confusion Matrix

```{r REPITOPEmatrix, message=FALSE,warning=FALSE,fig.width=6,dev='svg',fig.height=6,fig.cap="REpitope Confusion Matrix. Color is relative to sensitivity/specificity by proportional outcomes within reference groups"}

CM=confusionMatrix(positive = "Positive",mode = "prec_recall",reference=factor(combinedData %>% filter(Dataset %in% 'REPITOPE')  %>% select(Immunogenicity) %>% pull(),
                       levels = c("Negative","Positive")),
                       factor(combinedData %>% filter(Dataset %in% 'REPITOPE') %>% select(ImmunogenicityPrediction) %>% pull(),
                       levels=c("Negative","Positive")))
CM
table=data.frame(CM$table)

plotTable <- table %>%
  mutate(Performance = ifelse(table$Prediction == table$Reference, "Accurate", "Inaccurate")) %>%
  group_by(Reference) %>%
  mutate(prop = Freq/sum(Freq))


ggplot(data = plotTable, mapping = aes(x = Reference, y = Prediction, fill = Performance, alpha = prop)) +
  geom_tile() +
  geom_text(aes(label = Freq), vjust = .5, fontface  = "bold", alpha = 1,size=8) +
  scale_fill_manual(values = c(Accurate = "green", Inaccurate = "red")) +
  theme_bw() +
  xlim(rev(levels(table$Reference))) + ggtitle("REpitope")+ font("xy.text",size=16,color="black")+ font("xlab",size=16,color="black")+ font("ylab",size=16,color="black") + font("legend.text",size=10)


```
